---
title: "Project: qpNCA"
subtitle: "Purpose: compare results of qpNCA and Excel-based analysis"
author: Jan Huisman
date: March 2020
output:
  html_document:
    toc: true
    toc_depth: 3
--- 

## Load summary sheet from Excel-based parameter calculation

```{r}

InputDir="."

sum_excel=read_excel(paste(InputDir,"validation_qPNCA_1.0.12.xlsx",sep="/"),sheet="summ",guess_max = 100)

sum_excel = sum_excel |>
            select(-2) |> # remove empty column
            filter(!is.na(Parameter)) |>
            gather("rule","value",2:length(.)) |>
            spread(Parameter,value) |>
            mutate(id=as.numeric(id)) |>
            arrange(id) |>
            select(id,rule,everything()) |>
            gather("parameter","value_excel",-id,-rule,-dose,-factor,-includeCmax,-method,-reg,-route,-ss,-tau,-teval,-tstart,-tend) |>
            arrange(id,rule,parameter) |>
            mutate_at(vars(dose,factor,method,tau,teval,tstart,tend),as.numeric) |>
            mutate_at(vars(reg,ss),tolower) |>
            mutate(value_excel=ifelse(parameter=="intercept",exp(as.numeric(value_excel)),as.numeric(value_excel)))
            # exponentiate intercept before comparing to qPNCA result


# rename some parameters to match v1.0.22 terminology

sum_excel = sum_excel |>
            mutate_cond(condition=parameter=="cl.f.obs"&route=="IV"&ss=="n",parameter="cl.obs") |>
            mutate_cond(condition=parameter=="cl.f.obs"&route=="IV"&ss=="y",parameter="cl.ss") |>
            mutate_cond(condition=parameter=="cl.f.pred"&route=="IV"&ss=="n",parameter="cl.pred") |>
            mutate_cond(condition=parameter=="cl.f.pred"&route=="PO"&ss=="y",parameter="cl.f.ss") |>
            mutate_cond(condition=parameter=="cl.f.obs"&route=="PO"&ss=="y",value_excel=NA) |>
            mutate_cond(condition=parameter=="vz.f.obs"&route=="IV"&ss=="n",parameter="vz.obs") |>
            mutate_cond(condition=parameter=="vz.f.obs"&route=="IV"&ss=="y",parameter="vss.obs") |>
            mutate_cond(condition=parameter=="vz.f.pred"&route=="IV"&ss=="n",parameter="vz.pred") |>
            mutate_cond(condition=parameter=="vz.f.pred"&route=="IV"&ss=="y",parameter="vss.pred") |>
            mutate_cond(condition=parameter=="vss.obs"&route=="PO",value_excel=NA) |>
            mutate_cond(condition=parameter=="vss.pred"&route=="PO",value_excel=NA)


```

## Compare PO, SD results

```{r}

posd_qp = POSD$pkpar |>
          select(-area.back.extr,-r.squared,-calc.part,-calc.teval,-calc.tau,-t0.ok,-tlast.ok) |>
          gather("parameter","value_qp",-id,-dose,-includeCmax,-method,-reg,-route,-ss,-tau,-teval,-tstart,-tend) |>
          arrange(id,parameter) |>
          mutate(id=as.numeric(id))

posd_excel = sum_excel |>
             filter(id==-1|between(id,1,6)) |>
             mutate(route="ev")
             
# rounding

posd = left_join(posd_excel,posd_qp) |>
       mutate(value_qp_rounded=round(as.numeric(value_qp),4),
              value_excel_rounded=round(as.numeric(value_excel),4),
              identical=ifelse(value_excel_rounded==value_qp_rounded|
                               (is.na(value_excel_rounded)&is.na(value_qp_rounded)),1,0))

kable(posd)

```

### ***Result: There are `r nrow(posd|>filter(identical==0))` differences found between the qpNCA and Excel-based results.***

```{r echo=FALSE}

if (any(posd$identical==0,na.rm=TRUE)) { posd|>filter(identical==0)|>kable }

```

## Compare IV, SD results

```{r}
ivsd_qp = IVSD$pkpar |>
          select(-area.back.extr,-r.squared,-calc.part,-calc.teval,-calc.tau,-t0.ok,-tlast.ok) |>
          gather("parameter","value_qp",-id,-dose,-includeCmax,-method,-reg,-route,-ss,-tau,-teval,-tstart,-tend) |>
          arrange(id,parameter) |>
          mutate(id=as.numeric(id))

ivsd_excel = sum_excel |>
             filter(id==-2|between(id,7,10)) |>
             mutate(route="ivb")
             
# rounding

ivsd = left_join(ivsd_excel,ivsd_qp |> select(id,parameter,value_qp)) |>
       mutate(value_qp_rounded=round(as.numeric(value_qp),4),
              value_excel_rounded=round(as.numeric(value_excel),4),
                identical=ifelse(value_excel_rounded==value_qp_rounded|
                                (is.na(value_excel_rounded)&is.na(value_qp_rounded)),1,0))

kable(ivsd) 

```

### ***Result: There are `r nrow(ivsd|>filter(identical==0))` differences found between the qpNCA and Excel-based results.***

```{r echo=FALSE}

if (any(ivsd$identical==0,na.rm=TRUE)) { ivsd|>filter(identical==0)|>kable }

```

## Compare PO, MD no  steady state results

```{r}
pomdnoss_qp = POMDnoss$pkpar |>
              select(-area.back.extr,-r.squared,-calc.part,-calc.teval,-calc.tau,-t0.ok,-tlast.ok) |>
              gather("parameter","value_qp",-id,-dose,-includeCmax,-method,-reg,-route,-ss,-tau,-teval,-tstart,-tend) |>
              arrange(id,parameter) |>
              mutate(id=as.numeric(id))

pomdnoss_excel = sum_excel |>
                 filter(id==-3|between(id,11,17))
             
# rounding

pomdnoss = left_join(pomdnoss_excel,pomdnoss_qp|>select(id,parameter,value_qp)) |>
           mutate(value_qp_rounded=round(as.numeric(value_qp),4),
                  value_excel_rounded=round(as.numeric(value_excel),4),
                  identical=ifelse(value_excel_rounded==value_qp_rounded|
                                   (is.na(value_excel_rounded)&is.na(value_qp_rounded)),1,0))

kable(pomdnoss)

```

### ***Result: There are `r nrow(pomdnoss|>filter(identical==0))` differences found between the qpNCA and Excel-based results.***

```{r echo=FALSE}

if (any(pomdnoss$identical==0, na.rm=TRUE)) { pomdnoss|>filter(identical==0)|>kable }

```

## Compare PO, MD, steady state results

```{r}
pomdss_qp = POMDss$pkpar |>
            select(-area.back.extr,-r.squared,-calc.part,-calc.teval,-calc.tau,-t0.ok,-tlast.ok) |>
            gather("parameter","value_qp",-id,-dose,-includeCmax,-method,-reg,-route,-ss,-tau,-teval,-tstart,-tend) |>
            arrange(id,parameter) |>
            mutate(id=as.numeric(id))

pomdss_excel = sum_excel |>
               filter(between(id,18,20))
             
# rounding

pomdss = left_join(pomdss_excel,pomdss_qp|>select(id,parameter,value_qp)) |>
         mutate(value_qp_rounded=round(as.numeric(value_qp),4),
                value_excel_rounded=round(as.numeric(value_excel),4),
                identical=ifelse(value_excel_rounded==value_qp_rounded|
                                 (is.na(value_excel_rounded)&is.na(value_qp_rounded)),1,0))

kable(pomdss)

```

### ***Result: There are `r nrow(pomdss|>filter(identical==0))` differences found between the qpNCA and Excel-based results.***

```{r echo=FALSE}

if (any(pomdss$identical==0, na.rm=TRUE)) { pomdss|>filter(identical==0)|>kable }

```

###### END OF CODE (compare_results)
